Supplementary Materials

### 2020-06-08 analysis/analysis.Rmd
Tidying up and fixing some bugs

knitr::opts_chunk$set(echo = FALSE, message=FALSE, fig.align='center')

@@

@@

knitr::kable(index_table, caption = "subgroup index", escape = "F") %>% kableExtra::kable_styling(full_width = F)
```

```{r, fig.cap = "Symmetries present in each group."}
sym_dat <- read_csv("../subgroups/symmeries_in_group.csv") %>%
  mutate(group = str_to_upper(group))

knitr::kable(sym_dat, caption = "wallpaper group summary", escape = "F") %>% kableExtra::kable_styling(full_width = F)

@@

```{r define_comparison_summary_function}
comparison_summary <- function(subgroup_comp_dat, greater, measurement_lab) {
  # compute probabilties
  subgroup_comp_dat %>%
    group_by(key, index, normal) %>%
    summarise(
      mean_value = mean(value),
      prob_one_tailed = if_else(greater == TRUE, mean(value > 0), mean(value < 0)))  %>%
    mutate(
      prob_one_tailed = if_else(prob_one_tailed==0, 0.01, prob_one_tailed),
      measurement = measurement_lab,
      index_labs = as.numeric(as.factor(index)),
      lab_cols = v_cols[index_labs],
      prob_cat = cut(prob_one_tailed, c(0, 0.5, 0.75, 0.9, 0.99, 1))) -> comp_summary_dat

@@

```{r, fig.height=8, fig.cap="Distributions of the difference in mean log(rms) between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being greater than zero."}
# compute probabilties
comp_summary$eeg <- comparison_summary(subgroup_comp$eeg, TRUE, 'rms')

@@

@@

```{r ,fig.height=8, fig.cap="Distributions of the difference in mean log display duration threshold between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being less than zero."}

@@

```{r fig.height=8, echo = FALSE, fig.cap="Distributions of the difference in mean log(rms) between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being greater than zero."}

@@

```{r, fig.cap="This figure shows how many of our 64 comparisons are classed as having a greater-than-zero difference (less-than-zero for the display durations) for difference thresholds. between 0.5 an 1.0."}

@@

If we take p=0.95 as our cut-off, we can see that the subgroup relations are preserved in 56/64 = 87.5% and 49/64 = 76.6% of the comparisons for the primary EEG and display durations repectively. This compares to the $32/64= 50.0% and 22/64 = 34.4% for the control EEG conditions.

@@

```{r, cache=TRUE}
my_models <- list()
comp_summary$eeg$index <- as.numeric(as.character(comp_summary$eeg$index))
comp_summary$threshold$index <- as.numeric(as.character(comp_summary$threshold$index))

my_models$eeg <- brm(data = comp_summary$eeg, mean_value ~ index * normal)
my_models$disp <- brm(data = comp_summary$threshold, mean_value ~ index * normal)
summary(my_models$eeg)
summary(my_models$disp)
```

@@

```{r, fig.cap = "The effect of index and normality on log(rms) and log(ms)."}
comp_summary$eeg %>% 
  modelr::data_grid(index, normal) %>%
  add_fitted_draws(my_models$eeg, n = 100) %>%
  mutate(model = "primary eeg") -> d_plt_eeg

comp_summary$threshold %>% 
  modelr::data_grid(index, normal) %>%
  add_fitted_draws(my_models$disp, n = 100) %>%
  mutate(model = "psychophysical threshold") -> d_plt_disp

@@

```{r compare_comparisons, cache=TRUE}
bind_rows(
  select(comp_summary$eeg, measurement, key, mean_value),
  select(comp_summary$threshold, measurement, key, mean_value)) %>%
  spread(measurement, mean_value) -> d

@@

bayes_R2(m)
```

We can see that although the correlation is relatively weak, our confidence interval indicates that we can be reasonably positive that $R^2>0$ (i.e, 95\% credible interval is 0.026 - 0.302).

```{r fig.cap="Scatter plot showing the correlation between our two measures. Each line is a sample from the posterior of a Bayesian linear regression."}
d %>% 
  modelr::data_grid(rms = seq(-0.2, 0.8, 0.1)) %>%
  add_fitted_draws(m, n = 100) %>%
  ggplot(aes(x = rms, y = threshold, color = as.factor(index))) +
  geom_line(aes(y = .value, group = .draw), alpha = .1, colour = "thistle4") +
  geom_point(data = d) +
  theme_minimal() + 
  ggthemes::scale_colour_ptol("index")
```

>>>>

knitr::opts_chunk$set(echo = FALSE, message=FALSE, fig.align='center')
options(knitr.table.format = "html")

@@

Information on the symmetries and subgroups contained within each wallpaper group was obtained from <cite> and is summarised in the files `symmeries_in_group.csv`, `subgroup_relations.csv`, and `subgroup_normal.csv`.

<A short note on what is counted...i.e., so the reader understands that P2 has one rotation of order 2, etc>

```{r, fig.cap = "Symmetries present in each group."}

sym_dat <- read_csv("../subgroups/symmeries_in_group.csv") %>%
  mutate(group = str_to_upper(group))

knitr::kable(sym_dat, caption = "wallpaper group summary") %>% 
    kableExtra::kable_styling(full_width = F)
```

@@

knitr::kable(index_table, caption = "Summary of subgroup relationships. The numbers indicate the index of the subgroup, while italics indicate normal subgroups. Relationships written in yellow text are not included in our analysis.", escape = "F") %>% kableExtra::kable_styling(full_width = F)
```

We will remove identity relationships (i.e., a group is a subgroup of itself) and the three pairs of wallpapers groups that it subgroups of each other (e.g., PM is a subgroup of CM, and CM is a subgroup of PM). This leaves us with a total of `r nrow(subgroups)` subgroups to include in our analysis.

@@

```{r define_comparison_summary_function}

comparison_summary <- function(subgroup_comp_dat, greater, measurement_lab) {
  # compute probabilties
  subgroup_comp_dat %>%
    group_by(key, index, normal) %>%
    summarise(
      mean_value = mean(value),
      prob_one_tailed = if_else(greater == TRUE, mean(value > 0), mean(value < 0)))  %>%
    mutate(
      prob_one_tailed = if_else(prob_one_tailed==0, 0.01, prob_one_tailed),
      measurement = measurement_lab,
      index_labs = as.numeric(as.factor(index)),
      lab_cols = v_cols[index_labs],
      prob_cat = cut(prob_one_tailed, c(0, 0.5, 0.75, 0.9, 0.99, 1))) -> comp_summary_dat

@@

```{r, fig.height=8, fig.cap="Distributions of the difference in mean log(rms) between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being greater than zero.", cache=TRUE}

# compute probabilties
comp_summary$eeg <- comparison_summary(subgroup_comp$eeg, TRUE, 'rms')

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts

@@

```{r ,fig.height=8, cache = TRUE, fig.cap="Distributions of the difference in mean log display duration threshold between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being less than zero."}

@@

```{r fig.height=8, cache=TRUE, echo = FALSE, fig.cap="Distributions of the difference in mean log(rms) between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being greater than zero."}

@@

```{r, fig.cap="This figure shows how many of our 63 comparisons are classed as having a greater-than-zero difference (less-than-zero for the display durations) for difference thresholds. between 0.5 an 1.0."}

@@

If we take $p$=0.95 as our cut-off, we can see that the subgroup relations are preserved in 56/63 = 89% and 49/64 = 78% of the comparisons for the primary EEG and display durations repectively. This compares to the 32/64= 50% and 22/64 = 35% for the control EEG conditions.

@@

First of all, we run for the eeg rms data.

```{r, cache=TRUE}

# change index and normal variables to numeric for modelling
my_models <- list()

comp_summary$eeg %>% ungroup() %>%
   mutate(
     index = as.numeric(as.character(index)),
     normal = if_else(normal, 1, 0)) -> comp_summary$eeg

my_models$eeg <- brm(data = comp_summary$eeg, mean_value ~ index * normal)

summary(my_models$eeg)

And now for the display duration thresholds.

```{r, cache=TRUE}

# change index and normal variables to numeric for modelling

comp_summary$threshold %>% ungroup() %>%
   mutate(
     index = as.numeric(as.character(index)),
     normal = if_else(normal, 1, 0)) -> comp_summary$threshold

my_models$disp <- brm(data = comp_summary$threshold, mean_value ~ index * normal)

summary(my_models$disp)

@@

```{r, fig.cap = "The effect of index and normality on log(rms) and log(ms)."}
comp_summary$eeg %>%
  modelr::data_grid(index, normal) %>%
  add_fitted_draws(my_models$eeg, n = 100) %>%
  mutate(model = "primary eeg") -> d_plt_eeg
# 
comp_summary$threshold %>% 
   modelr::data_grid(index, normal) %>%
   add_fitted_draws(my_models$disp, n = 100) %>%
   mutate(model = "psychophysical threshold") -> d_plt_disp

@@

```{r compare_comparisons, cache=TRUE}
bind_rows(
  select(comp_summary$eeg, measurement, key, mean_value, index),
  select(comp_summary$threshold, measurement, key, mean_value, index)) %>%
  spread(measurement, mean_value) -> d

@@

bR2 <- bayes_R2(m)

print(bR2)

We can see that although the correlation is relatively weak, our confidence interval indicates that we can be reasonably positive that $R^2>0$ (i.e, 95\% credible interval is `r round(bR2[3],2)` - `r round(bR2[4], 2)`).

```{r fig.cap="Scatter plot showing the correlation between our two measures. Each line is a sample from the posterior of a Bayesian linear regression."}

d %>%
  modelr::data_grid(rms = seq(-0.2, 1, 0.1)) %>%
  add_fitted_draws(m, n = 100) %>%
  ggplot(aes(x = rms, y = threshold, color = as.factor(index))) +
  geom_line(aes(y = .value, group = .draw), alpha = .1, colour = "thistle4") +
  geom_point(data = d) +
  theme_minimal() +
  ggthemes::scale_colour_ptol("index")
